A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-12 manuscript.Rmd
remove duplicated sentence
show required sample size and bias of sim in PAC

<!-- define replicability and then... 
 define reproducibility -->
Even worse, researchers might often not even be able to achieve reproducibility---defined as the ability to obtain identical results from the *same* data with the *same* computer code.
Over the past decades, computational statistical methods have radically changed the ability of researchers from all disciplines to process and analyze data with complex statistical models.
With these advances came challenges that contribute to broader concerns of irreproducibility in the published literature, among them the lack of exact and unambiguous documentation of computational methods and each computational step taken.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves [@vanlissa2020worcs].
Only with access to both data and procedures can we guarantee full computational reproducibility, meaning that the creations emanating from a given data analysis (a statistical result or an entire manuscript describing the results) can be exactly reproduced at any time in the future, by any person, and on any computer.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves [@vanlissa2020worcs].

@@

PAC works well within this reproducible framework.
First, the preregistration becomes a part of the reproducible repository.
It is part of the set of version-controlled files and provides transparency about when the preregistration file, data files, and code files were changed over the course of a research project.
If code was version-controlled and tagged (see Section XXX) before data collection, all deviations from the preregistration or any post-hoc additions that were performed after data collection are transparent and are visible and comparable in the version history.

One way to ensure that you can expect your analysis to work with real data is to simulate data.
A data simulation allows you to verify that the code runs error-free and lets you form more realistic expectations about the estimates' correctness and precision.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `missing_rcode_simulation` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `missing_rcode_simulation`%.
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.

>>>>

<!-- define replicability and then... 
 define reproducibility -->
Even worse, researchers might often not even be able to achieve reproducibility---defined as the ability to obtain identical results from the *same* data with the *same* computer code.
Over the past decades, computational statistical methods have radically changed the ability of researchers from all disciplines to process and analyze data with complex statistical models.
With these advances came challenges that contribute to broader concerns of irreproducibility in the published literature, among them the lack of exact and unambiguous documentation of computational methods and each computational step taken.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves [@vanlissa2020worcs].
Only with access to both data and procedures can we guarantee full computational reproducibility, meaning that the creations emanating from a given data analysis (a statistical result or an entire manuscript describing the results) can be exactly reproduced at any time in the future, by any person, and on any computer.

@@

PAC works well within this reproducible framework.
First, the preregistration becomes a part of the reproducible repository.
It is part of the set of version-controlled files and provides transparency about when the preregistration file, data files, and code files were changed over the course of a research project.
If code was version-controlled and tagged (see Section [Git]) before data collection, all deviations from the preregistration or any post-hoc additions that were performed after data collection are transparent and are visible and comparable in the version history.

One way to ensure that you can expect your analysis to work with real data is to simulate data.
A data simulation allows you to verify that the code runs error-free and lets you form more realistic expectations about the estimates' correctness and precision.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `r minn$n_obs` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `r round((est_diff - true_diff)*100/true_diff, 2)`%.
These results are also visualized in Figure \@ref(fig:simulation-plot).
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.
